---
title: "Carolina Data Challenge: Hurricane Harvey"
author: "Christian Taylor"
date: "September 16, 2017"
output: html_document
---
```{r}
library(tidyverse)
library(dplyr)
library(maps)
library(mapdata)
library(readr)
Harvey_tweets <- read_csv("C:/Users/taylorch/OneDrive/Carolina Data Challenge/carolinadata-hurricane-harvey/Harvey_tweets.csv")
needs <- read_delim("C:/Users/taylorch/OneDrive/Carolina Data Challenge/carolinadata-hurricane-harvey/needs.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
shelters <- read_delim("C:/Users/taylorch/OneDrive/Carolina Data Challenge/carolinadata-hurricane-harvey/shelters.csv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
```
```{r}
location <- select(needs, are_supplies_needed, are_volunteers_needed, longitude, latitude)

supplies_vol <- filter(location, are_supplies_needed %in% c("True", "False"), are_volunteers_needed %in% c("True", "False"), longitude, latitude)
supplies_vol
```



```{r}
map("state", "Texas", col = "lightskyblue", fill = TRUE)
```

```{r}
map("state", "Texas", xlim = c(-100, -90), ylim = c(25, 32), col = "lightskyblue", fill = TRUE)
```

##Map of Needs

```{r}
map("state", "Texas", xlim = c(-97, -93), ylim = c(28, 31), col = "grey90", fill = TRUE)
points(supplies_vol$longitude, supplies_vol$latitude, pch=19, col="blue", cex=.5)
```

*Blue = A location that communicated its needs*

###Map of Needs (Color Coordinated)

```{r}
both_sv <- filter(supplies_vol, are_supplies_needed == "True", are_volunteers_needed == "True")
neither_sv <- filter(supplies_vol, are_supplies_needed == "False", are_volunteers_needed == "False")
s_notv <- filter(supplies_vol, are_supplies_needed == "True", are_volunteers_needed == "False")
nots_v <- filter(supplies_vol, are_supplies_needed == "False", are_volunteers_needed == "True")


map("state", "Texas", xlim = c(-97, -93), ylim = c(28, 31), col = "grey90", fill = TRUE)
points(both_sv$longitude, both_sv$latitude, pch=19, col="red", cex=0.5)
points(s_notv$longitude, s_notv$latitude, pch=19, col="darkgreen", cex=0.5)
points(nots_v$longitude, nots_v$latitude, pch=19, col="darkorange", cex=0.5)
points(neither_sv$longitude, neither_sv$latitude, pch=19, col="orchid", cex=.5)
```

*Red = Location in need of both Supplies and Volunteers*
*Orchid = Location in need of neither Supplies nor Volunteers*
*Green = Location in need of Supplies, but not Volunteers*
*Orange = Location in need of Volunteers, but not Supplies*

##Map of Shelters Across United States

```{r}
shel_locations <- filter(shelters, accepting == "True" | accepting == "False", latitude, longitude)
map("worldHires", "usa", xlim = c(-125, -65), ylim = c(25, 50), col = "gray90", fill = TRUE)
points(shel_locations$longitude, shel_locations$latitude, pch=19, col="violet", cex=0.5)
```

*Purple = Hurricane Shelter*

##Map of Shelters in the Texas-Louisiana Region
```{r}
accepting_shel <- filter(shel_locations, accepting == "True")
not_accepting_shel <- filter(shel_locations, accepting == "False")
map("state", "Texas", xlim = c(-107, -88), ylim = c(25, 37), col="gray90", fill = TRUE)
map("state", "Louisiana", xlim = c(-107, -88), ylim = c(25,37), col = "gray90", fill = TRUE, add = TRUE)
points(accepting_shel$longitude, accepting_shel$latitude, pch=19, col="blue", cex=0.3)
points(not_accepting_shel$longitude, not_accepting_shel$latitude, pch=19, col="red", cex=0.3)
```

*Blue = Shelter accepting more people.*
*Red = Shelter no longer accepting people.*

##Map of Shelters around the Greater Houston Area
```{r}
map("state", "Texas", xlim = c(-97, -93), ylim = c(28, 31), col = "gray90", fill = TRUE)
map("state", "Louisiana", xlim = c(-97, -93), ylim = c(28,31), col = "gray 90", fill = TRUE, add = TRUE)
points(accepting_shel$longitude, accepting_shel$latitude, pch=19, col="blue", cex=0.4)
points(not_accepting_shel$longitude, not_accepting_shel$latitude, pch=19, col="red", cex=0.4)
```

*Blue = Shelter accepting more people.*
*Red = Shelter no longer accepting people.*
